On the relation of the entanglement spectrum to the Zak-phase

### 2020-05-27 draft.tex
Update 27-5
Updated Fig. 5 with a case where the simple method does not work and added a bit of text to go with it. Update Fig.6 and rewrote parts of Appendix C with added new figures that we should discuss.

Let us also discuss an alternative way of computing Zak phase. 
Using the fact that $N_A = \Tr C_A$, we can rewrite $\chi$ as
\begin{equation}
\chi = \left(\sum_{i\in r} \xi_i\right) \, {\rm mod} \, 1.
\end{equation}
A simpler way to compute this quantity is by obtaining $C_A$ for an open chain, labeled as $C_A^{ o}$. 
For a sufficiently long  chain the right eigenvalues will remain the same, %as we still place a virtual cut in the middle of the chain 
but the left eigenvalues will no longer be present. 
This allows one to simply compute
\begin{equation}
\chi = \Tr C_A^{o} \, {\rm mod} \, 1.
\end{equation}
This method, however, will introduce a stronger finite size effect and requires substantially larger systems for the same accuracy. 
In addition, it only works for homogeneous systems as explained below.

@@

In reference \cite{Zaletel2014} translational invariance was used to derive the relation between the many-body entanglement spectrum and the Zak phase. If this symmetry is broken by, for example, by adding weak disorder to the system, this will modify slightly the eigenvalues of the reduced density matrix but not the charge assignment in Eq.~\eqref{zaletel} in the Appendix. The left side of Eq.~\eqref{zaletel} will be cut independent while the right side is not, and therefore cannot be correct.

We are interested therefore in finding a cut-independent quantity from the EOS that might still result in the Zak phase. The first thing one can do is to do an average over the different cuts. Naively one would cut-average the expression in Eq.~\eqref{eq_loc}, however the average of a circular quantity is not well defined. We defined $\chi$ modulo 1 because it is a phase, but it also served the purpose of getting rid of arbitrary charge assignment of some of the modes close to 1, which is problematic. We define
\begin{equation}
\chi_s = \frac{1}{2} \left( \sum_{i\in r}\xi^s_i-\sum_{i\in l}\xi^s_i  + N_A \right),
\end{equation}
obtained for cuts at sites $s$ and $s+L/2$. The cut-average is then given by
\begin{equation}
\bar{\chi} = \left(\frac{1}{L}\sum_{s=1}^L \chi_s \right)\, \rm{mod} \, 1.
\label{batcutavg}
\end{equation}
As we move through the different cuts the average position of  the eigenstates at 1 can move slightly, so that the number of states at each half of the system depends on the cut, which will affect the cut-average. In order to obtain the correct result of  the contribution of the states at $\xi=1$ should be constant across cuts, so that it can be correctly cancelled by the modulo 1. Therefore we have to find a way of correcting for jumps of $1$ in $\chi_s$ when a mode at one crosses the $L/4$.

%
%In reference \cite{Zaletel2014} translational invariance was used to derive the relation between the many-body entanglement spectrum and the Zak phase. If this symmetry is broken by, for example, adding weak disorder to the system, this will modify slightly the eigenvalues of the reduced density matrix but not the charge assignment in Eq.~\eqref{zaletel} in the Appendix. The left side of Eq.~\eqref{zaletel} will be cut independent while the right side is not, and therefore cannot be correct. 
%
%We are interested therefore in finding a cut-independent quantity from the ES that might still result in the Zak phase. The first thing one can do is to do an average over the different cuts. Naively one would cut-average the expression in Eq.~\eqref{loceq}, however the average of a circular quantity is not well defined. We defined $\chi$ modulo 1 because the Zak phase is also defined modulo 1, but it also served the purpose of getting rid of the sign choice for the bulk modes, which is problematic. As we do for the edge state, we can choose a sign for the bulk modes in the following way
%\begin{equation}
%g_i=
%\begin{cases}
% +1 &,\rm{if} \expval{\hat{X}}_i > L/4  \\
% -1 &,\rm{if} \expval{\hat{X}}_i < L/4.
%\end{cases}
%\end{equation}
%So that now we define
%\begin{equation}
%\chi_s = \frac{1}{2} \left( \sum_{i\in r}\xi^s_i-\sum_{i\in l}\xi^s_i + \sum_{i\in b}g_i^s \xi^s_i  + N_A \right),
%\end{equation}
%obtained for cuts at $s$ and $s+L/2$ and the cut-average is given by
%\begin{equation}
%\bar{\chi} = \frac{1}{L}\sum_{s=1}^L \chi_s.
%\label{batcutavg}
%\end{equation}
%By adding the perturbation proportional to $C_A\hat{X} C_A$ the bulk modes also localize. As we move through the different cuts the average position of the bulk modes moves slightly. For most modes this will not affect the assigned sign, but for the modes near the middle of subsystem $A$ it might be that for strong enough inhomogeneity that the mode crosses $L/4$ and the sign changes. We find that in order for us to get the correct result the contribution from the bulk modes should be constant across cuts, so we have to find a way of correcting for these jumps of $1$ in $\chi_s$.

\subsubsection{Continuous inhomogeneity}
$\chi$ does not have to be continuous, but jumps of 'integers' can be compensated by hand.

In the case we have a continuous inhomogeneity one can obtain a new quantity $\chi'_s$ with a constant bulk contribution, by assuming that the discontinuities of $\chi_s$ above some threshold, $h$, are due to these unphisical changes of sign for the bulk states and eliminating them by shifting it by an integer number so that
\begin{equation}
\chi_{s+1}'-\chi'_s < h
\end{equation}
and it is continuous. $\chi'_s$ can now be cut-averaged to obtain the Zak phase. In figure \ref{inh} we show this for a continuous profile for $\kappa_s$. We see that $\chi_s$ in fact presents jumps of $1$ but once we correct them in $\chi'_s$, its cut average results in the Zak phase. We also see the same for a disordered $\kappa_s$. Even though the disorder is relatively strong we see that $\chi_s'$, after the artificial jumps are eliminated, is fairly continuous, which allows us to use this method even for strong inhomogeneity, as long as we can identify this jumps.

\begin{figure}[h!]

\centering
\makebox[0pt]{
\subfloat[]{
  \includegraphics[width=40mm]{4_a.pdf}
  \label{inha}
}
\subfloat[ ]{
  \includegraphics[width=40mm]{4_b.pdf}
}
}\hspace{0mm}

\makebox[0pt]{
\subfloat[]{
  \includegraphics[width=40mm]{4_c.pdf}
}
\subfloat[]{
  \includegraphics[width=40mm]{4_d.pdf}
}
}\hspace{0mm}

\makebox[0pt]{
\subfloat[]{
  \includegraphics[width=40mm]{4_e.pdf}
}
\subfloat[]{
  \includegraphics[width=40mm]{4_f.pdf}
}
}

\caption{Using the parameters \label{inh}$t=1,t'=2,m =1$, we show our results for two different profiles for $\kappa_s$, one continuous (a) and one with disorder (b). In (c) and (d) we show the ES (black) and $ \chi_s \, {\rm mod} \, 1$ (green). In (e) and (f) we show $\chi_s$ (green), $\chi'_s$ (blue dots), $\gamma$ (red) and $\expval{\chi'_s}_{\rm cuts}$ (blue dashed) }

\end{figure}

In some cases, this calculation simplifies a bit more. Note that, in the case where one can tell a priori that the width of $\chi'_s$ is lower than 1, as in the example with disorder, to recover $\chi_s'$ one can simply take the modulo 1 and adding an offset, so for instance in the example with disorder we can obtain
\begin{equation}
\chi'_s = ([\chi_s-1/2] \, {\rm mod} \, 1)+1/2.
\end{equation}
One can then cut-average the resulting $\chi_s \, \rm{mod} \,1$ in the same way to obtain the Zak phase. This cannot be done in the first example because as we already see in Fig.\ref{inh}.c, $\chi_s \, \rm{mod} \,1$ wraps aroud the full range, so that there is no offset that will allow us to average it in a well-defined way.

In Fig.\ref{disorder} we show $1-\expval{\chi_s}_{\rm cuts}/\gamma$ for different system lengths for system with weak disorder, as well as the disorder average of $1-\chi_0/\gamma$. For both cases the error seems to vanish in the thermodynamic limit. For small systems both errors are very similar, which suggests that it comes strictly from a systematic finite size error in the computation of either the Zak phase or the ES which is system-independent. For larger systems the disoder average is more dispersed, probably due to the number of configurations considered not being high enough.

\begin{figure}[h]
\centering
\makebox[0pt]{
\subfloat[$t = 1, t' = 2, m=1, \kappa_s \in (-1,1)$]{
  \includegraphics[width=65mm]{disvscut.pdf}
}
}
\caption{We show $1-\expval{\chi_s'}_{\rm cuts}/\gamma$ (red) and $1-\expval{\chi_s'}_{\rm dis}/\expval{\gamma}_{\rm dis}$. The cut average seems to do as good or better than the disorder average. For small systems it seems that both errors are similar, pointing to a systematic finite size error in the computation of either the Zak phase or the ES. For larger systems the error in the disorder average is more spread, which suggests that one should average more configurations.}
\label{disorder}
\end{figure}

\subsubsection{Wannier states, L/4 crossing fix}

\begin{figure}[t]
\centering
\makebox[0pt]{
\subfloat[$\expval{\hat{X}}_{i,s}$ for different cuts, for the entanglement eigenstates such that $\xi_i < 1/2$ (black) and the Wannier states (red)]{
  \includegraphics[width=90mm]{loca.pdf}
}}\hspace{0mm}

\makebox[0pt]{
\subfloat[$\chi_s$]{
  \includegraphics[width=45mm]{wan1.pdf}
}
\subfloat[$\chi_s'$ ]{
  \includegraphics[width=45mm]{wan2.pdf}
}
}

\caption{For the same parameters as used in Fig.5.a,c,e we show the expectation value of the position for the ES eigenstates (black) and the Wannier states (red), showing that the latter are a good approximation of the former in the bulk. We highlight by a continuous red line the bulk mode that crosses $L/4$ which causes the jumps in $\chi_s$. In (b) we show again $\chi_s$ (black) and the correction for the sign switch (red). In (c) $\chi_s'$ is reconstructed via this method, showing the same result as we had before.}
\label{wan}
\end{figure}

In a general case where the discontinuities are too strong and we do not know how to correct for these jumps as explained before one has to take a closer look into the bulk states to ensure a consistent sign assignment. As we mentioned above the bulk states farthest away from the edges are the problematic ones. They are also the ones best approximated by the Wannier states obtained from the chain with periodic boundary conditions, as the eigenstates of 
\begin{equation}
C\hat{X}_{\rm PBC}C
\end{equation}
where $\hat{X}_{\rm PBC} = \exp\{i 2\pi \hat{X}/L\}$. Similar to when we go through different cuts labeled by $s$, we now consider the Wannier states dependent on where we define our lattice site 1, shifted by $s$. The obtained Wannier states for $s$ and $s+1$ will be therefore exactly the same, but shifted one lattice site. By considering their average position $\expval{\hat{X}_{PBC}}_{i,s}$ we can define a set of $2L$ Wannier states that depend continuously on $s$, provided that the Hamiltonian is continuous. These Wannier states are then a good approximation for the Bulk states of $C_A$ we find for the different cuts. 
Consider now the quantity $\sum_i\expval{\hat{X}}_{i,s}$. So far everything was $s$ independent as our system was periodic, but by considering the operator $\hat{X}$ we introduce an unphysical boundary so that it will depend on how the lattice sites are defined. If the states do not cross this unphysical boundary then $\sum_i\expval{\hat{X}}_{i,s} = \sum_i\expval{\hat{X}_{\rm PBC}}_{i,s} $ and it will be a constant with $s$. However, when a Wannier state crosses the boundary we obtain the same constant plus $L$. If we put this boundary at $L/4$ the quantity 
\begin{equation}
\delta_s = \frac{1}{L}\left(\sum_i\expval{\hat{X}}_{i,s}-\sum_i\expval{\hat{X}}_{i,0}\right)
\end{equation}
will be 1 (0) when a states has crossed the boundary or 0 (-1) when it has not, depending on the number of states in A at $s=0$, which we take as reference. Depending which state we take as reference will introduce a global integer shift for all cuts, so it is not relevant as it will go away after we average and take the modulo 1. By adding this term to our cut-average we will compensate for when our bulk state in the middle of A crosses $L/4$ and its charge changes, leading to a continuous $\chi_s'$ which can be averaged,
\begin{equation}
\chi_s' = \chi_s + \delta_s
\end{equation}

In Fig.\ref{wan} we show how this works for the same continuous example as in \ref{inh}. In Fig.\ref{wan}.a we show the expectation value of the position operator for both the entanglement eigenstates (in black) and the Wannier states (in red) for different values of $s$. In Fig.\ref{wan}.b and c we show $\chi_s$, which displays jumps due to a bulk state crossing $L/4$, and $\delta_s$, showing that it properly corrects the sign switch.

This method conceptually works perfectly whenever the bulk states of the ES are equal to the Wannier states, i.e. in the thermodynamic limit, but it is not clear what the small parameter is. It depends on the $\lambda$ used (it should be small enough to not affect ES but large enough to localize the ES eigenstates) but also on the system. Systems with many ES edge modes close to the bulk tend to have a higher finite size effect.

We also find that whenever there is an interphase in our system, and therefore a zero mode in the energy spectrum, the Wannier states are not necesseraly a good approximation of the bulk of finite systems. However, in the cases where we have an interphase but $\chi_s$ is fairly continuous, so that we can correct these jumps, cut-averaging results again in the Zak phase.

As the sign assigned to the bulk modes becomes relevant in the inhomogeneous case one might think that it is better to use the open chain, $\chi_s = \Tr C_A^{o,s}$, as one avoids the issue of having to assign any signs at all. Although this is true we find another problem. By adiabatically tuning down the coupling between the $L$ and $1$ sites we see that the eigenvalues of the $left$ modes flow to either $0$ or $1$. In the case where this eigenvalues oscillate around $1/2$ for different cuts this leads to discontinuities in the number of bulk modes at $\xi=1$ which again result in an incorrect cut-average and we found no practical way of compensating for these discontinuitiesyfgh.

@@

The proof in Ref.\cite{Zaletel2014} also breaks down for superconducting systems. However, as we did for systems without translational invariance, one can extend this identity for systems with pairing terms as well. Since one computes the Zak phase from the single-particle Bogoliubov-de Gennes Hamiltonian, we can obtain the correspondent ES and everything discussed above should apply as well. Take for example the kitaev chain, with the following Hamiltonian
\begin{align*}
H =& -\mu \sum_{i} c_i^\dagger c_i - t \sum_{i}\left( c_{i+1}^\dagger c_i + {\rm h.c.}\right) \\
&+  \sum_{i}\left( \Delta c_{i} c_{i+1} + {\rm h.c.}\right).
\end{align*}
Using the spinor $\phi_i^\dagger = (c_i^\dagger, c_i)$, we can rewrite the Hamiltonian as
\begin{align*}
&H = \frac{1}{2}\sum_i \phi^\dagger_i H_{BdG,ij} \phi_j,\\
&H_{BdG,ij} = -\mu \tau_z \delta_{ij} - (t \tau_z + i\Delta \tau_y )\delta_{i,j+1}- (t \tau_z - i\Delta \tau_y)\delta_{i,j-1}.
\end{align*}
Note that by taking $t' = \kappa = \kappa = 0$ in the BDI model, Eq. \ref{bdi_model}, we obtain
\begin{align*}
H_{ij} =& m \sigma_x\delta_{ij} + \frac{1}{2} t \left[(\sigma_x + i \sigma_y)\delta_{i,j+1} + (\sigma_x - i \sigma_y) \delta_{i,j-1} \right],
\end{align*}
which is just the Bogoliubov-de Gennes Hamiltonian of the Kitaev chain by rotating $x$ into $z$ and identifying $\mu = -m, t_{\rm Kit} = -t_{BDI}/2, \Delta = -t_{BDI}/2 $. From Fig.\ref{bdi_phase_diagram} we see that the $BDI$ model transitions from $\nu = 1$ to the trivial phase at $t=0, m=\pm t_{BDI}$, or alternatively, when $\mu = \pm 2 t_{Kit}$, which is the known result for the Kitaev chain. Therefore the results already shown for the BDI model studied here are also applicable to the Kitaev chain.

@@

>>>>

Let us also discuss an alternative way of computing Zak phase. 
Using the fact that $N_A = \Tr C_A$, we can rewrite $\chi$ as
\begin{equation}
\chi = \left(\sum_{i\in r} \xi_i\right) \, {\rm mod} \, 1.
\label{eq:chihom}
\end{equation}
A simpler way to compute this quantity is by obtaining $C_A$ for an open chain, labeled as $C_A^{ o}$. 
For a sufficiently long  chain the right eigenvalues will remain the same, %as we still place a virtual cut in the middle of the chain 
but the left eigenvalues will no longer be present. 
This allows one to simply compute
\begin{equation}
\chi = \Tr C_A^{o} \, {\rm mod} \, 1.
\end{equation}
This method, however, will introduce a stronger finite size effect and requires substantially larger systems for the same accuracy. 
In addition, it only works for homogeneous systems as explained below.

@@

In reference \cite{Zaletel2014} translational invariance was used to derive the relation between the many-body entanglement spectrum and the Zak phase. If this symmetry is broken by adding, for example, weak disorder, this result is no longer true. However we found, as our main result, that one can still obtain the Zak phase as the cut-average of the relation derived for homogeneous systems. For some systems this can be written as (\carlos{not sure about this phrasing})
\begin{align}
\gamma =\left(\frac{1}{L}\sum_{s=1}^L (\chi_s \, \rm{mod} \, 1)\right)\, \rm{mod} \, 1,
\label{eq:inh_simple}
\end{align}
where
\begin{equation}
\chi_s = \frac{1}{2} \left( \sum_{i\in r}\xi^s_i-\sum_{i\in l}\xi^s_i  + N_A \right)
\end{equation}
is obtained for cuts at sites $s$ and $s+L/2$. In Fig.\ref{fig:simple_inh}.b we show the same system as in Fig.\ref{2}.c with an added moderate disorder in the $\kappa$ parameter shown in \ref{fig:simple_inh}.a . We show the EOS of one cut with that particular $\chi_s$, which differs from the Zak phase. The Zak phase is shown to be recovered by the cut-average of $\chi$. Next we show the results for the same system with $m=-2$, and a continuous profile for $\kappa$ shown in \ref{fig:simple_inh}.c. In Fig. \ref{fig:simple_inh}.d is shown how the EOS and $\chi_s$ depends on the cuts, and how the Zak phase is again recovered by the cut-averaged $\chi$.

\begin{figure}[h!]
\centering
\makebox[0pt]{
\subfloat[$\kappa_i$]{
  \includegraphics[width=35mm]{4cdisorderkap.pdf}
}
\subfloat[$t=1,t'=-2,s=0$]{\includegraphics[width=35mm]{4cdisorderES.pdf}
}
}\hspace{0mm}

\makebox[0pt]{
\subfloat[$\kappa_i$]{
  \includegraphics[width=35mm]{simplecutkap.pdf}
}
\subfloat[$t=1,t'=-2,m=2$]{\includegraphics[width=35mm]{simplecutES.pdf}
}
}\hspace{0mm}

\makebox[0pt]{
\subfloat[$\kappa_i$]{
  \includegraphics[width=35mm]{cutavgwrongkap.pdf}
}
\subfloat[$t=1,t'=-2,m=1$]{\includegraphics[width=35mm]{cutavgwrong.pdf}
}
}
\caption{In a) and b) we show the system in Fig. 4.c with an added disorder. we show the ES (black) and $ \chi_s \, {\rm mod} \, 1$ (green) for one particular cut,$\gamma$ (red) and $\expval{\chi_s}_{\rm cuts}$ (blue dashed). In c) and d) we show the same system at $m=2$ and a continuous homogeneous profile for $\kappa_i$. In e) and f) we show a case where using \eqref{eq:inh_simple} fails. We show the ES and $\chi_s$ for all cuts. }
\label{fig:simple_inh}
\end{figure}

We have shown two cases were using expression \ref{eq:inh_simple} leads to the correct result. The average of a circular quantity is in fact not uniquely defined, and the average we do in Eq.\ref{eq:inh_simple}, which equates to averaging the valus in $(0,1)$ around $1/2$ (\carlos{is this clear?}), is just one choice that works in this cases. However in Fig.\ref{fig:simple_inh}.f this cut-average fails to give the Zak phase. This happens because by taking $\chi$ modulo 1 we have thrown out relevant information.
To avoid this issue we can instead take the cut-average 
\begin{align}
\gamma =\left(\frac{1}{L}\sum_{s=1}^L \chi_s \right)\, \rm{mod} \, 1,
\label{eq:inh_fixed}
\end{align}

but this however has to be done carefully. So far we have naively separated our eigenstates into \emph{left} and \emph{rigth} sectors, assigned the charges acordingly, and took the modulo 1 to eliminate the contribution of the bulk modes that localize at the center of A. The problem resides in the classification of these bulk modes. Even if the rest of the EOS remains constant, due to the inhomogeneity a bulk mode can cross the middle of region A, as shown in Fig.\ref{fig:loc_fix}, which will change $\chi$ by $1/L$, even though choosing $L/4$ as the separation between the \emph{left} and \emph{rigth} sectors is not physical. In order for \ref{eq:inh_fixed} to work properly the contribution from the bulk modes, which should vanish in the end, must remain constant across the different cuts. In order to achieve this we choose a cut-dependent threshold that the bulk modes do not cross, $l_s$, as the mean position of two of the eigenstates close to this middle point of A, as shown in Fig.\ref{fig:loc_fix}. This is done in practice for the Wannier states (\carlos{Do I explain exactly how do I do it numerically?}).
Note that in the thermodynamic limit it does not matter if the position of these eigenstates cross as they are degenerate, the only important thing is that the number of bulk modes at each sector remains constant (\carlos{Not sure about this phrasing either}).

\begin{figure}[h!]
\centering
\includegraphics[width=70mm]{loc_fix.pdf}
\caption{Average position of the Wannier states in red and, slightly shifted, the localized entanglement eigenstates (\carlos{rename $C_A+\lambda C_A X C_A$?} in blue. In black we show the threshold $l_s$ obtained as the mean value of the two Wannier states close de $19$ and $20$) $L=80,\lambda=10^{-6}, t = 1, t'= 2, m=0$}
\label{fig:loc_fix}
\end{figure}

As the sign assigned to the bulk modes becomes relevant in the inhomogeneous case one might think that it is better to use the open chain, $\chi_s = \Tr C_A^{o,s}$, as one avoids the issue of having to assign any signs at all. Although this is true we find another problem. By adiabatically tuning down the coupling between the $L$ and $1$ sites we see that the eigenvalues of the $left$ modes flow to either $0$ or $1$. This can lead to discontinuities in the number of bulk modes at $\xi=1$ which again result in an incorrect cut-average. \carlos{Works in some cases.}

@@

However, as we did for systems without translational invariance, one can extend this identity for systems with pairing terms as well. Since one computes the Zak phase from the single-particle Bogoliubov-de Gennes Hamiltonian, we can obtain the correspondent ES and everything discussed above should apply as well. Take for example the kitaev chain, with the following Hamiltonian
\begin{align*}
H =& -\mu \sum_{i} c_i^\dagger c_i - t \sum_{i}\left( c_{i+1}^\dagger c_i + {\rm h.c.}\right) \\
&+  \sum_{i}\left( \Delta c_{i} c_{i+1} + {\rm h.c.}\right).
\end{align*}
Using the spinor $\phi_i^\dagger = (c_i^\dagger, c_i)$, we can rewrite the Hamiltonian as
\begin{align*}
&H = \frac{1}{2}\sum_i \phi^\dagger_i H_{BdG,ij} \phi_j,\\
&H_{BdG,ij} = -\mu \tau_z \delta_{ij} - (t \tau_z + i\Delta \tau_y )\delta_{i,j+1}- (t \tau_z - i\Delta \tau_y)\delta_{i,j-1}.
\end{align*}
Note that by taking $t' = \kappa = \kappa = 0$ in the BDI model, Eq. \ref{bdi_model}, we obtain
\begin{align*}
H_{ij} =& m \sigma_x\delta_{ij} + \frac{1}{2} t \left[(\sigma_x + i \sigma_y)\delta_{i,j+1} + (\sigma_x - i \sigma_y) \delta_{i,j-1} \right],
\end{align*}
which is just the Bogoliubov-de Gennes Hamiltonian of the Kitaev chain by rotating $x$ into $z$ and identifying $\mu = -m, t_{\rm Kit} = -t_{BDI}/2, \Delta = -t_{BDI}/2 $. From Fig.\ref{bdi_phase_diagram} we see that the $BDI$ model transitions from $\nu = 1$ to the trivial phase at $t=0, m=\pm t_{BDI}$, or alternatively, when $\mu = \pm 2 t_{Kit}$, which is the known result for the Kitaev chain. Therefore the results already shown for the BDI model studied here are also applicable to the Kitaev chain.

@@

\section{$\lambda$ term}

In order to ensure that we obtain localized entanglement eigenstates,  we diagonalize $C_A^\lambda = C_A + \lambda/L^2 C_A\hat{X}C_A$ instead of $C_A$, where $\lambda$ is our small parameter and the reason we include the $L^2$ scaling will be explained below.
For the whole system one way of obtaining localized eigenstates of the full correlation function (\carlos{also the Hamiltonian?}) is to diagonalize $C\hat{X}C$, which results in localized Wannier states. $C$ commutes with this operator because it is a projector, but this is no longer the case for $C_A$. Far from the edges however, $C_A$ and $C$ are equivalent, so that the states close to $\xi=1$ will perfectly localize into Wannier states by adding the $\lambda$ term. Note that in the thermodynamic limit the operator $\hat{X}$ acts as proportional to an identity for localized states. Therefore in this limit the localized eigenstates of $C_A$ far from $\xi = 0,1$ are also eigenstates of $C_A^\lambda$ while their mixture is not. Threfore this operator breaks all degeneracies of $C_A$ and results in localized eigenstates.

One has to be careful when choosing the correct $\lambda$. A parameter $\lambda$ which is too small will fail to break the degeneracies and localize the eigenstates. On the other hand the $\lambda$ term will  modify the eigenvalues and introduce an additional error to $\chi$. Assuming localized eigenstates we have $\expval{\hat{X}}_{i\alpha} \simeq i$. Therefore the error it introduces in $\chi$ is roughly
\begin{equation}
\frac{\lambda}{L^2} \sum_{\alpha=1,2}\left( \sum_{i=L/4+1}^{L/2}i-\sum_{i=1}^{L/4}i \right) = \frac{\lambda }{8},
\end{equation}
it is proportional to $\lambda$ and independent on system size. In Fig.\ref{lambdaL} we show this error in $\chi$ together with the maximum width of the eigenstates in the top half of the spectrum (\carlos{as we only care about the midgap states and the bulk modes at 1}), for different system sizes. We see that indeed the error remains constant with system size. In this case most of the bulk modes are above $\xi = 1-10^{-10}$, so that the error coming from the $\lambda$ term is bigger than the one we make by failing to localize the bulk modes. However, by looking at the maximum width of the eigenstates we see three different regions. One region at low system size where the width increases linearly. A second region where the system localizes and the width seems constant, and finally for large systems a third region where the width increases again because the $\lambda$ term is too small to break the degeneracies and localize the eigenstates.

\begin{figure*}[h!]
\centering
\makebox[0pt]{
\subfloat[${\rm Log}_{10}(\chi - \gamma)$ (\carlos{There are errors at $-5,-9,-12$ because that's the order of the eigenvalue of the bulk modes that should cancel pairwise but dont due to failure of localization. Furthermore, the error in yellow around $L=150$ is due to a mode close  to $\xi = 0$ so that it does not appear in Fig. b.})]{
  \includegraphics[width=55mm]{lambdaL1.pdf}
}
\subfloat[${\rm Max}\bra{\psi_i}\sigma_x\ket{\psi_i}$ for $\xi_i >1/2$. \carlos{I don't know why the green line localizes so bad. I have to look further into it}]{\includegraphics[width=55mm]{lambdaL2.pdf}
}
}
\caption{$t = 1, t'= 2, m=0$ for $-{\rm Log}_{10}[\lambda] = 4,5,6,7,8,9,10$.}
\label{lambdaL}
\end{figure*}

In Fig.\ref{linearRegion} we take a closer look into the first region with a maximum width proportional to the system size. What happens in this region is that due to finite size the midgap modes that localize in the edges overlap so the resulting eigenstates are not localized and are split from $\xi = 1/2$. The boundary where this region ends changes with $\lambda$ and coincides with the point where the splitting from the $\lambda$ term is bigger than the splitting due to finite size. The gap between these midgap modes that mix starts decreasing with larger system size up to a point, where the system starts to localize, where this splitting is roughly constant with system size and proportional to $\lambda$. In the $\nu = 1$ region the two midgap states are degenerate and we do not observe this first linear region, the eigenstates localize for any finite $\lambda$.

\begin{figure*}[h!]
\centering
\makebox[0pt]{
\subfloat[Width of the eigenstate closest to $\xi=1/2$]{
  \includegraphics[width=55mm]{linearBoundary.pdf}
}
\subfloat[Gap between the two eigenstates closest to $\xi = 1/2$]{\includegraphics[width=55mm]{linearBoundarysplit.pdf}
}
}
\caption{$t = 1, t'= 2, m=0, \nu=0 , -{\rm Log}_{10}[\gamma] = 4,5,6,7,8,9,10$ for the different colors. Vertical lines are addded to better show how the features of both plots match.}
\label{linearRegion}
\end{figure*}

For inhomogeneous systems the story is slightly different. Due to the cut-average a wrong assignment of the bulk modes leads to an error of order $\mathcal{O}(1/L)$. In Fig. \ref{lambdainh} we have the error made in $\chi$ and the maximum width of the eigenstates for different values of system size $L$. The disorder does not change anything discussed above and we observe the same behavior in the localization as in the homogeneous case.

\begin{figure*}[h!]
\centering
\makebox[0pt]{
\subfloat[${\rm Log}_{10}(\chi - \gamma)$ ]{
  \includegraphics[width=55mm]{lambdaLinherr.pdf}
}
\subfloat[${\rm Max}\bra{\psi_i}\sigma_x\ket{\psi_i}$ for $\xi_i >1/2$.]{\includegraphics[width=55mm]{lambdaLinhloc.pdf}
}
}
\caption{$t = 1, t'= 2, m=0, \nu=2$. }
\label{lambdainh}
\end{figure*}
